---
output:
  html_document: default
  pdf_document: default
---

```{r clean_start, warning=FALSE, include=FALSE}
rm(list = ls())

## Load required libraries 
require(lme4)
require(tidyverse)

ProPer_MSA_scores <- read.csv("data_tables/ProPer_MSA_scores.csv")

# Create subsets: by syllable
data_A_stress <- droplevels(filter(ProPer_MSA_scores, syllable=="A_A*" | syllable=="A_P*"))
data_A_final <- droplevels(filter(ProPer_MSA_scores, syllable=="A_F"))
data_N_stress <- droplevels(filter(ProPer_MSA_scores, syllable=="N_P*"))
data_N_final <- droplevels(filter(ProPer_MSA_scores, syllable=="N_F"))
data_ab <- droplevels(filter(ProPer_MSA_scores, syllable=="ab"))

# https://youtu.be/SY3Kxf7ZTeI
```

# Concertos for Multiple Violins (phase 2)
<!-- [^1] -->

### Distributions of ProPer metrics

#### MSA Team 037

***

<!-- ## Synchrony plots -->
<!-- F0 shape within syllables -->

<!-- ***Synchrony*** interpretation: falling < 0 < rising -->

<!-- ```{r plotSyncBYsyll, warning=FALSE, echo=FALSE} -->
<!-- # , include=FALSE -->
<!--   ggplot(data_A_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = sync_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-20, 20)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("Synchrony: Adjective stressed syllable (A_A*/A_P*)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("Synchrony (%)") -->

<!--   ggplot(data_A_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = sync_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-20, 20)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("Synchrony: Adjective final syllable (A_F)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("Synchrony (%)") -->

<!--   ggplot(data_N_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = sync_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-20, 20)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("Synchrony: Noun stressed syllable (N_P*)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("Synchrony (%)") -->

<!--   ggplot(data_N_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = sync_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-20, 20)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("Synchrony: Noun final syllable (N_F)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("Synchrony (%)") -->

<!--   ggplot(data_ab, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = sync_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-20, 20)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("Synchrony: ab(legen)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("Synchrony (%)") -->

<!-- ``` -->

<!-- ## ∆F0 plots -->
<!-- F0 change between syllables -->

<!-- ***∆F0*** interpretation: lower < 0 < higher -->

<!-- ```{r plotDeltaF0bySyll, warning=FALSE, echo=FALSE} -->
<!-- # , include=FALSE -->
<!--   ggplot(data_A_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = DeltaF0_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-75, 75)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("∆F0: Adjective stressed syllable (A_A*/A_P*)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("∆F0 (%)") -->

<!--   ggplot(data_A_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = DeltaF0_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-75, 75)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("∆F0: Adjective final syllable (A_F)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("∆F0 (%)") -->

<!--   ggplot(data_N_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = DeltaF0_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-75, 75)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("∆F0: Noun stressed syllable (N_P*)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("∆F0 (%)") -->

<!--   ggplot(data_N_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = DeltaF0_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-75, 75)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("∆F0: Noun final syllable (N_F)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("∆F0 (%)") -->

<!--   ggplot(data_ab, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = DeltaF0_rel)) + -->
<!--   geom_violin(width = .9) + -->
<!--   geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   ylim(-75, 75)+ -->
<!--   stat_summary(fun = "mean", shape = 3, size = 1)+ -->
<!--   theme_classic()+ -->
<!--   scale_color_discrete(name = "typicality")+ -->
<!--   ggtitle("∆F0: ab(legen)") + -->
<!--   xlab("Noun")+ -->
<!--   ylab("∆F0 (%)") -->

<!-- ``` -->

## Mass plots
Prosodic strength (duration X power) of syllabic intervals

***Mass*** interpretation: weaker < 1 < stronger

```{r plotMassBYsyll, warning=FALSE, echo=FALSE}

  # ggplot(data_A_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = mass_rel)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 1) +
  # ylim(0, 3)+
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Mass: Adjective stressed syllable (A_A*/A_P*)") +
  # xlab("Noun")+
  # ylab("Mass (relative scale)")
  # 
  # ggplot(data_A_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = mass_rel)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 1) +
  # ylim(0, 3)+
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Mass: Adjective final syllable (A_F)") +
  # xlab("Noun")+
  # ylab("Mass (relative scale)")
  # 
  # ggplot(data_N_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = mass_rel)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 1) +
  # ylim(0, 3)+
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Mass: Noun stressed syllable (N_P*)") +
  # xlab("Noun")+
  # ylab("Mass (relative scale)")
  # 
# NFsPlot <-
  ggplot(data_N_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = mass_rel)) +
  geom_violin(width = .9) +
  geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  geom_hline(yintercept = 1) +
  ylim(0, 3)+
  stat_summary(fun = "mean", shape = 3, size = 1)+
  theme_classic()+
  scale_color_discrete(name = "typicality")+
  ggtitle("Mass: Noun final syllable (N_F)") +
  xlab("Noun")+
  ylab("Mass (relative scale)")
# print(NFsPlot)
# ggsave(NFsPlot, file=paste0("plots/NFpositionMass.pdf"),device=cairo_pdf)
  
  # ggplot(data_ab, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = mass_rel)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 1) +
  # ylim(0, 3)+
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Mass: ab(legen)") +
  # xlab("Noun")+
  # ylab("Mass (relative scale)")

```

## Duration plots 
Duration of syllabic intervals

Absolute values  
(200 ms marked for typical average syllable)

```{r plotDurationBYsyll, warning=FALSE, echo=FALSE}

  # ggplot(data_A_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 200) +
  # ylim(0, 400) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Duration: Adjective stressed syllable (A_A*/A_P*)") +
  # xlab("Noun")+
  # ylab("Duration (ms)")
  # 
  # ggplot(data_A_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 200) +
  # ylim(0, 400) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Duration: Adjective final syllable (A_F)") +
  # xlab("Noun")+
  # ylab("Duration (ms)")
  # 
  # ggplot(data_N_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 200) +
  # ylim(0, 400) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Duration: Noun stressed syllable (N_P*)") +
  # xlab("Noun")+
  # ylab("Duration (ms)")

  ggplot(data_N_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = intervalDuration)) +
  geom_violin(width = .9) +
  geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  geom_hline(yintercept = 200) +
  ylim(0, 400) +
  stat_summary(fun = "mean", shape = 3, size = 1)+
  theme_classic()+
  scale_color_discrete(name = "typicality")+
  ggtitle("Duration: Noun final syllable (N_F)") +
  xlab("Noun")+
  ylab("Duration (ms)")

  # ggplot(data_ab, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y = intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = 200) +
  # ylim(0, 400) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Duration: ab(legen)") +
  # xlab("Noun")+
  # ylab("Duration (ms)")

```

## Power plots
Periodic energy means of syllabic intervals

Periodic energy in a normalized (0--1) logarithmic scale  
(0.5 marked for scale's median)

```{r plotPowerBYsyll, warning=FALSE, echo=FALSE}

  # ggplot(data_A_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y =  mass/intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = .5) +
  # ylim(0, 1) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Power: Adjective stressed syllable (A_A*/A_P*)") +
  # xlab("Noun")+
  # ylab("Periodic energy (normalized dB)")
  # 
  # ggplot(data_A_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y =  mass/intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = .5) +
  # ylim(0, 1) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Power: Adjective final syllable (A_F)") +
  # xlab("Noun")+
  # ylab("Periodic energy (normalized dB)")
  # 
  # ggplot(data_N_stress, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y =  mass/intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = .5) +
  # ylim(0, 1) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Power: Noun stressed syllable (N_P*)") +
  # xlab("Noun")+
  # ylab("Periodic energy (normalized dB)")

  ggplot(data_N_final, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y =  mass/intervalDuration)) +
  geom_violin(width = .9) +
  geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  geom_hline(yintercept = .5) +
  ylim(0, 1) +
  stat_summary(fun = "mean", shape = 3, size = 1)+
  theme_classic()+
  scale_color_discrete(name = "typicality")+
  ggtitle("Power: Noun final syllable (N_F)") +
  xlab("Noun")+
  ylab("Periodic energy (normalized dB)")

  # ggplot(data_ab, aes(x = factor(target_name, level = c("Gurke", "Kirsche", "Moehre",  "Trauben", "Erbsen", "Bohnen", "Walnuss", "Zitrone")), y =  mass/intervalDuration)) +
  # geom_violin(width = .9) +
  # geom_jitter(aes(col = typicality), position = position_jitter(width = 0.2), size = 1) +
  # geom_hline(yintercept = .5) +
  # ylim(0, 1) +
  # stat_summary(fun = "mean", shape = 3, size = 1)+
  # theme_classic()+
  # scale_color_discrete(name = "typicality")+
  # ggtitle("Power: ab(legen)") +
  # xlab("Noun")+
  # ylab("Periodic energy (normalized dB)")

```
